---
title: "p8105_hw5_hz2771"
author: 'Haolin Zhong (UNI: hz2771)'
date: "2021/11/18"
output: github_document
---

## Dependencies

```{r}
library(tidyverse)
library(purrr)
```


## Problem 2

### Create dataframe

```{r}
lgtd = tibble(
  filenames = list.files("./data/")
)
```

### Read in data iteratvely

```{r}
lgtd = 
  lgtd %>% 
  mutate(
    filepaths = str_c("./data/", filenames)    
  ) %>% 
  mutate(
    data = map(filepaths, read_csv)
  )
```

### Tidy the result

```{r}
lgtd_tidy = 
  lgtd %>% 
  mutate(
    filenames = str_replace(filenames, ".csv", ""),
    group = str_sub(filenames, 1, 3)
  ) %>% 
  unnest() %>% 
  pivot_longer(names_to = "week", 
               values_to = "value", 
               cols = "week_1":"week_8") %>% 
  mutate(
    week = str_replace(week, "week_", ""),
    week = as.numeric(week)
  ) %>% 
  select(subject = filenames, group, week, value)
```

### Make the spaghetti plot

```{r}
lgtd_tidy %>% 
  ggplot(aes(x = week, y = value, group = subject, color = group)) +
  geom_path() +
  geom_point() +
  scale_color_viridis_d()
```

Through the plot, we can observe two obvious trends:

- In experiment group, the values of subjects increased over time in a approximate linear style, while in control group value of subjects basically stay stable.

- In both groups, within the group, subject with relatively high initial value end with relatively high value, and subjects with relatively low initial value end with relatively low value.
